A Context Menu for the Real World: Controlling Physical Devices Through Head-Worn Infrared Targeting

### 2013-09-18 doc/sigchi14/targeting.tex
more refinements

\subsection{Participants}
We recruited 15 participants from our institution. 13 had never used Glass before. 4 wore prescription glasses, which may have affected their task performance as wearing glasses beneath Glass makes it more cumbersome to secure the position of Glass and to adjust the screen to the optimal angle.

@@

\subsubsection{Preference}
Eleven of 15 users preferred infrared mode over list mode (three preferred list, one was undecided). While both interfaces were judged similarly on overall ease of connecting, list navigation was also perceived to be cumbersome (see Figure~\ref{fig:target-likert}). As self-report data can easily skew positive as participants try to please experimenters, we also asked participants to elucidate why they preferred one interface over the other.

>>>>

\subsection{Participants}
We recruited 14 participants from our institution. 13 had never used Glass before. 4 wore prescription glasses, which may have affected their task performance as wearing glasses beneath Glass makes it more cumbersome to secure the position of Glass and to adjust the screen to the optimal angle. Half of them performed {\em infrared} mode first and the other half did {/em list} mode first.

@@

\subsubsection{Preference}
Eleven of 14 users preferred infrared mode over list mode (three preferred list, one was undecided). While both interfaces were judged similarly on overall ease of connecting, list navigation was also perceived to be cumbersome (see Figure~\ref{fig:target-likert}). As self-report data can easily skew positive as participants try to please experimenters, we also asked participants to elucidate why they preferred one interface over the other.
